---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(cache)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# cache - Caching function outputs

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pmcharrison/cache?branch=master&svg=true)](https://ci.appveyor.com/project/pmcharrison/cache)
[![Travis build status](https://travis-ci.org/pmcharrison/cache.svg?branch=master)](https://travis-ci.org/pmcharrison/cache)
[![Coverage status](https://coveralls.io/repos/github/pmcharrison/cache/badge.svg)](https://coveralls.io/r/pmcharrison/cache?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

`cache` is an R package for function output caching, or memoisation.

The [memoise](https://cran.r-project.org/web/packages/memoise/index.html) package 
is an effective tool for caching repeated computations in data analysis projects.
However, the memoise package cannot (easily) memoise 
internal functions within R packages,
especially when the demand is for file-based memoisation,
or when memoisation options need to be exposed to the end user.

This package addresses these problems.
It is designed for memoising functions when creating R packages,
while allowing subsequent package users to control cache options
(e.g. disabling cache, clearing the cache, changing the cache directory).

## Installation

You can install the package directly from Github.

``` r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("pmcharrison/cache")
```
## Example usage

Define a simple cached function:

```{r}
f <- function(x, ...) cache({
  message("Computing...")
  c(x, rnorm(1))
}, ...)
```

The first time it's called, the main body of the function is run.

```{r}
f(1) 
```

The second time it's called, the result is loaded from the file-based cache.

```{r}
f(1)
```

Our function `f` can be called with various caching options - 
see `?cache::cache` for details. 
These options include:

- `.cache` - Whether or not to use cache on the current call.
- `.cache_memory` - Enables in-memory caching.
- `.cache_dir` - Directory in which to save cached files.
- `.cache_force` - If TRUE, an error will be thrown if the current call
cannot be found in the cache. Useful for debugging.

If we call `f` with cache disabled, we should get a different result.

```{r}
f(1, .cache = FALSE) # produces a different result
```

We can also define an in-memory cache. 
In-memory caches are faster than the default file-based caches.

```{r}
x <- cache_memory()
f(1, .cache_memory = x)

f(1, .cache_memory = x)

as.list(x)[[1]]
```

When we're done, we can clear the cache.

```{r}
clear_cache()
```
